Molecular dynamics simulation of a driven synchronized particle

### 2021-03-29 manuscript/manuscript_ajp_version2.tex
updated title

\title{Molecular dynamics simulation of synchronization in driven particles}

@@

  A working example of this code is available
  in Ref.~\cite{supplemental}.
  If you would like to write your own,
  the following guide
  will walk you through our choices.
  In the code excerpts below,
  most comments and optional details are removed for clarity.

@@

  The molecular dynamics
  described above
  is available in Ref.~\cite{supplemental}.
  We use the Python programming
  language
  for educational purposes.
  To model additional particles,
  the authors recommend a more traditional 
  compiled coding language
  to perform the many operations associated
  with neighbor lists to compute particle interactions.

@@

\item[(a)]
  Explore the effect of increasing $F_{\rm ac}$ on the hopping pattern.
  For a single driven particle,
  the hopping patterns are typically characterized
  by $n_f$, the number of forward steps,
  versus $n_b$, the number of backward steps  in one
  time period.
  The total displacement of $(n_f - n_b) \lambda$ 
  is the net hop length.  
  In Fig.~\ref{fig:2_Fd_vy_time},
  the particle moves forward through a minima ($n_f = 1$),
  and does not move backward through a full minima ($n_b = 0$).  
  To achieve
  backward hops,
  the driving parameters must have
  a ratio of $F_{\rm ac}/F_{\rm dc} > 1$ 
  and a difference $|F_{\rm ac} - F_{\rm dc}| > A_p$.
  Holding all other parameters fixed,
  explore how the hopping pattern
  changes for increasing $F_{\rm ac}$.
  For example,
  what pattern of hops occurs for
  fixed parameters 
  $f=0.01$, $F_{\rm dc}=0.07$, and $A_p = 0.1$
  and
  modified parameter
  $F_{\rm ac} = 0.2, 0.3$ and $0.4$?

>>>>

%DM replace?
%\title{Molecular dynamics simulation of synchronization in driven particles}
\title{Molecular dynamics simulation of a driven synchronized particle}

@@

  A working example of this code is available
  in Ref.~\cite{supplemental}
  If you would like to write your own,
  the following guide
  will walk you through our choices.
  In the code excerpts below,
  most comments and optional details are removed for clarity.

@@

  %The molecular dynamics
  %described above
  %is available in Ref.~\cite{supplemental}
  We use the Python programming
  language
  for educational purposes.
  To model additional particles,
  the authors recommend a more traditional 
  compiled coding language
  to perform the many operations associated
  with neighbor lists to compute particle interactions.

@@

\item[(a)]
  Explore the effect of increasing $F_{\rm ac}$ on the hopping pattern.
  For a single driven particle,
  the hopping patterns are typically characterized
  by $n_f$, the number of forward steps,
  versus $n_b$, the number of backward steps  in one
  time period.
  The total displacement of $(n_f - n_b) \lambda$ 
  is the net hop length.  
  In Fig.~\ref{fig:2_Fd_vy_time},
  the particle moves forward through a minima ($n_f = 1$),
  and does not move backward through a full minima ($n_b = 0$).  
  To achieve
  backward hops,
  the driving parameters must have
  a ratio of $F_{\rm ac}/F_{\rm dc} > 1$ 
  and a difference $|F_{\rm ac} - F_{\rm dc}| > A_p$.
  Holding all other parameters fixed,
  explore how the hopping pattern
  changes for increasing $F_{\rm ac}$.
  For example,
  calculate the patterns of hops for
  fixed parameters 
  $f=0.01$, $F_{\rm dc}=0.07$, and $A_p = 0.1$
  and
  modified parameter
  $F_{\rm ac} = 0.2, 0.3$ and $0.4$.
